### 2013-12-13 manuscripts/reply/reply.tex
Updating reply ms.
Incorporating changes made in `short-repy.tex` into `reply.tex` and
`reply-main.tex`. Leaving `short-reply.tex` in repo, because Mark has
been working on this copy.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    with low likeihood and high prior density that is imposed by broad uniform
    priors.
    \citet{Hickerson2013} have responded to this work, questioning the priors
    used by \citet{Oaks2012} and presenting an approximate Bayesian
    model-averaging approach that uses narrow, empirically informed uniform
    priors.
    \citet{Hickerson2013} use this method to re-analyze the empirical dataset
    of \citet{Oaks2012} comprised of 22 pairs of vertebrate populations from
    the Philippines, and conclude the model-averaging approach circumvents the
    issues revealed by \citet{Oaks2012} and yields robust inference of
    divergence models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of low marginal likelihoods of parameter-rich models.
    Here we discuss an error in the methodology of \citet{Hickerson2013} that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate that the approach of \citet{Hickerson2013} is
    biased toward models with less parameter space, which manifests in a strong
    tendency to sample predominantly from models that exclude the true values
    of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show the approach of \citet{Hickerson2013} is still biased toward
    inferring simultaneous divergences even when the true divergences are
    randomly distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    low marginal likelihoods of complex models is a primary cause of the bias
    of \msb toward models with less parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using questionable
    empirically informed uniform priors.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes}

}

@@

%CWL:
% \highLight{The goal of this paper needs to be to highlight the major
%     differences of opinion on how ABC can be used in comparative phylogeography
%     and how these changes to msbayes can be made that will improve the
%     inference in the future. We should avoid nit-picking the Hickerson paper
%     and try to stay positive.}
\input{reply-main.tex}

\section*{Acknowledgments}
We thank the National Science Foundation for supporting this work (DEB
1011423).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.

\bibliography{../bib/references}
% \bibliography{references}

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    were affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probabilities of models in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the prior and
    that the inference method had low power to detect variation in divergences
    times.
    These results were not surprising, in light of a rich statistical literature
    showing that the marginal likelihood of a model is sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times, leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically
    informed uniform priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an empirical
    Bayesian stance for this model-choice problem, because it can mislead model
    posterior probabilities, which are inherently measures of belief in the
    models after prior knowledge is updated by the data.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide interpretation of results.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes} 
}

@@

\input{reply-main.tex}

\section*{Acknowledgments}
We thank Jake Esselstyn for insightful comments that greatly improved this
work.
J.\ Oaks thanks the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.

\bibliography{../bib/references}
